draft-data

### 2024-11-23 descriptivestry.Rmd
modelestimates-GOFs-desresults-darkgraph

<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>My Descriptives</title>
    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->

</head>
</html>

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

# Getting started
```{r clean}
rm(list = ls())
```

## Packages
```{r package}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

#install.packages("data.table")
require(data.table)  # mainly for faster data handling
# install.packages('xml2')
require(xml2)
# install.packages('rvest')
require(rvest)
require(igraph)
require(ggraph)

@@

@@

Functions chunk 
```{r functions 1}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

More functions
```{r functions 2}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

Scholar data
```{r scholar data}
scholars <- fload("./data/processed/scholars_20240924.rda") 
#make sure to lead fload first of course
```

```{r saving schoalr output}
# save the output of your function

test  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = c("sociology", "political science"),
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("all")) # all, first, last # which ties in there

# USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
# usually first author has most prestige
```

Ego data
```{r df_ego data}
df_ego <- fload("./data/processed/df_ego_20241108.rda")

@@

# Descriptives

@@

descriptives (mean etc.) in whole sample
```{r sum gender}
summary(df_ego$gender)
```

gender counts across whole sample (0 = female, 1 = male)
```{r counts gender-all}
table(df_ego$gender)
```

overall gender distribution in sample
```{r}
# Create the histogram
ggplot(df_ego, aes(x = gender))+
  geom_bar(color = "darkgrey", fill ="#B3DE69", width = 0.75)+
  labs(title = "Histogram of Gender", x = "Gender\n (0 = female, 1 = male)", y = "Count") + theme(plot.title = element_text(hjust = 0.5, face = "bold"))

@@

Genders per department (0 = female, 1 = male)
```{r gender per dep.}

@@

descriptives (mean etc.)
```{r summary h index}
summary(df_ego$h_index)
```
Overall  (INSERT YEARS STILL)
```{r hist h index}
# Histogram of prestige scores for Wave 1 
hist(df_ego$h_index, breaks = 30, main = "Distribution of H-Index from yearX to yearX",     xlab = "H Index", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

H index per department
```{r table per dep h index}
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```

## Ego network

### basic descriptives

Nr. of nodes
```{r nodes}
vcount(test_w1)
```

Nr. of edges
```{r edges}
ecount(test_w1)
```

Dyad census
    ```{r dyad cen}

igraph::dyad_census(test_w1)
    ```

Triad-census
    ```{r triad cen}
igraph::triad_census(test_w1)
    ```

Edge-density
    ```{r edge dens}
# edge density
igraph::edge_density(test_w1)
    ```

### more in depth:

reciprocity
    ```{r recip}
reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
    ```
reciprocity = 1 makes sense since the ties are undirected rn

degree centrality / degreee?
    ```{r degree}

degree_testw1 <- degree(test_w1)
degree_testw1 <- as.data.frame(degree_testw1)
ggplot(degree_testw1, aes(as.numeric(degree_testw1), colour = as.numeric(degree_testw1) )) +
  geom_histogram(binwidth = .9) +
  labs(
    title = "Distribution Degrees Wave 1",
    x = "Distribution of Degrees",
    y = "Count"  ) +
  ylim(0, 65)

@@

Betweenness centrality /betweenness?
    ```{r betweenness}
betweenness_w1 <- igraph::betweenness(test_w1, directed = T)
betweenness_w1 <- as.data.frame(betweenness_w1)
ggplot(betweenness_w1, aes(as.numeric(betweenness_w1), colour = as.numeric(betweenness_w1))) +
  geom_histogram(binwidth = 1.2) +
  labs(
    title = "Distribution Betweenness Wave 1",
    x = "Distribution of Betweenness",
    y = "Count")

Clustering
    ```{r clustering}
#clustering w1
clustering_w1 <- igraph::transitivity(test_w1, type = "local")
clustering_w1 <- as.data.frame(clustering_w1)
ggplot(clustering_w1, aes(as.numeric(clustering_w1), colour = as.numeric(clustering_w1) )) +
  geom_histogram(binwidth = .05) +
  labs(
    title = "Distribution Clustering Wave 1",
    x = "Distribution of Clustering",
    y = "Count" )
    ```

## Network-level descriptives

Density
    ```{r density}
density_w1 <- igraph::edge_density(test_w1)
density_w1
    ```

Average path length
    ```{r path length}
mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
    ```

Segregation
    - Mortons I
    - also graphs below
```{r plot}

plot(test_w1,
     vertex.label = NA,
     edge.width = 0.2,
     edge.arrow.size =0.2)
```

### Plotting: Gender - igraph
#### with isolates
```{r plot gender}
# names(df_ego) #see labels of variables

plot(test_w1,
     vertex.color = ifelse(df_ego$gender == 1, "#FFED6F", "#80B1D3"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
  vertex.label = NA,
  vertex.size = 7.5,
  edge.width = 0.5,
  edge.arrow.size = 0.1,
  main = "Network with isolates [yellow = female, blue = male]")

# if you dont want plot to turn, save the layout (look at SNASS)
```

#### without isolates
```{r removing isolates}
indegr_w1 <- igraph::degree(test_w1, mode = "in")

isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]

noisolates_w1 <- delete_vertices(test_w1, isolates_w1)

gsize(noisolates_w1) # edges

gorder(noisolates_w1) # vertices
```

```{r plot wo isolates}
plot(noisolates_w1,
  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
  # here: if gender = 1 (aka man) then red dot, if not then blue 
  vertex.label = NA,
  vertex.size = 9,
  vertex.frame.color = "black",
  edge.curved = 0.2,
  edge.arrow.size = 0.3,
  edge.color = "gray",
  edge.width = 0.2,
  main = "Network without isolates [yellow = female, blue = male]")
```

### Plotting: h-index -ggraph
Credits to Hannah Groennou for the basis of the code of these graphs. 
#### with isolates ?
```{r}

indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

#set size of plot
options(repr.plot.width = 15, repr.plot.height = 18)

#plot wave 1 with isolates
p_iso <- ggraph(test_w1,
       layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = h_index)) + 
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_iso + labs(title = "Network with isolates",
        subtitle = "Plot of indegree and H-index",
        caption = "Data refer to: Scholars RU sociology and political science departments") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
```

#### without isolates
```{r}

indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

#set size of plot
options(repr.plot.width = 15, repr.plot.height = 15)

#plot wave 1 without isolates 
p_noiso <- ggraph(noisolates_w1,
       layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.7) +
  geom_node_point(aes(size = indegree, color = h_index)) + 
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_noiso + labs(title = "Network without isolates",
        subtitle = "Plot of indegree and H-index",
        caption = "Data refer to: Scholars RU sociology and political science departments") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))

# allowed values for the font face include: “plain”, “italic”, “bold” and “bold.italic”.

##### H-index per department
```{r}
indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
# assign discipline to scholar
V(test_w1)$discipline <- df_ego$discipline.24

V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

#set size of plot
options(repr.plot.width = 15, repr.plot.height = 15)

#plot wave 1 without isolates 
p_noiso <- ggraph(noisolates_w1,
       layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.7) +
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(discipline))) + 
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_noiso + labs(title = "Departments without isolates",
        subtitle = "Plot of indegree and H-index",
        caption = "Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))

# allowed values for the font face include: “plain”, “italic”, “bold” and “bold.italic”.

### Plotting gender - ggraph 
#### with isolates per department 
```{r}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender

# assign discipline to scholar
V(test_w1)$discipline <- df_ego$discipline.24

V(test_w1)$indegree <- indegr_w1

p_gender <- ggraph(test_w1,
  layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  theme_void()

p_gender + labs(title = "Departments with isolates",
        subtitle = "Plot of indegree and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))

#### without isolates per department 
```{r}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender

# assign disciplines to scholars
V(test_w1)$discipline <- df_ego$discipline.24
V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

p_noisgender <- ggraph(noisolates_w1,
  layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  theme_void()

p_noisgender + labs(title = "Departments without isolates",
        subtitle = "Plot of indegree and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))

### Plotting h index and gender -ggraph
#### with isolates 
```{r}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender
# V(test_w1)$gender <- ifelse(df_ego$gender >= 0.5,1,0)

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

p_gender <- ggraph(test_w1,
  layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_gender + labs(title = "Network with isolates",
        subtitle = "Plot of indegree, H-index and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))

#### without isolates

```{r gen without iso}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

p_noisogender <- ggraph(noisolates_w1,
  layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_noisogender + labs(title = "Network without isolates",
        subtitle = "Plot of indegree, H-index and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))

# Detour: Colors

```{r mypalette, include = FALSE, eval = FALSE, hide = TRUE}
# palette i like:
palette("Set 3");  sinplot("Set 3")
palette.swatch("Set 3")
palette.colors(palette = "Set 3")
 "#8DD3C7" "#FFFFB3" "#BEBADA" "#FB8072" "#80B1D3" "#FDB462"
 "#B3DE69" "#FCCDE5" "#D9D9D9" "#BC80BD" "#CCEBC5" "#FFED6F"
```

```{r colors in R, include = TRUE, eval = FALSE, hide = TRUE}
colors (distinct = TRUE) # prints all colors R knows
palette.pals()
#  [1] "R3"              "R4"              "ggplot2"        
#  [4] "Okabe-Ito"       "Accent"          "Dark 2"         
#  [7] "Paired"          "Pastel 1"        "Pastel 2"       
# [10] "Set 1"           "Set 2"           "Set 3"          
# [13] "Tableau 10"      "Classic Tableau" "Polychrome 36"  
# [16] "Alphabet"

palette.colors(palette = "-palette name here-")
# [1] "#000000" "#E69F00" "#56B4E9" "#009E73" "#F0E442" "#0072B2"
# [7] "#D55E00" "#CC79A7" "#999999"
```

```{r look at colors PLOT, include = TRUE, eval = FALSE, hide = TRUE}
## Demonstrate the colors 1:8 in different palettes using a custom matplot()
sinplot <- function(main=NULL, n = 8) {
    x <- outer(
	seq(-pi, pi, length.out = 50),
	seq(  0, pi, length.out = n),
	function(x, y) sin(x - y)
    )
    matplot(x, type = "l", lwd = 4, lty = 1, col = 1:n, ylab = "", main=main)
}
sinplot("default palette")

palette("R3");        sinplot("R3")
palette("Okabe-Ito"); sinplot("Okabe-Ito")
palette("Tableau")  ; sinplot("Tableau", n = 10) # i like 
palROB <- colorRampPalette(c("red", "darkorange2", "blue"), space = "Lab")
palette(palROB(16)); sinplot("palROB(16)", n = 16) # the orange purple blue rainbow retro vibe yay 
palette("default") # reset
```

```{r look at colors SWATCH, include = TRUE, eval = FALSE, hide = TRUE}
palette.swatch <- function(palette = palette.pals(), n = 8, nrow = 8,
                           border = "black", cex = 1, ...)
{
     cols <- sapply(palette, palette.colors, n = n, recycle = TRUE)
     ncol <- ncol(cols)
     nswatch <- min(ncol, nrow)
     op <- par(mar = rep(0.1, 4),
               mfrow = c(1, min(5, ceiling(ncol/nrow))),
     	       cex = cex, ...)
     on.exit(par(op))
     while (length(palette)) {
 	subset <- seq_len(min(nrow, ncol(cols)))
 	plot.new()
 	plot.window(c(0, n), c(0.25, nrow + 0.25))
 	y <- rev(subset)
 	text(0, y + 0.1, palette[subset], adj = c(0, 0))
 	y <- rep(y, each = n)
 	rect(rep(0:(n-1), n), y, rep(1:n, n), y - 0.5,
 	     col = cols[, subset], border = border)
 	palette <- palette[-subset]
 	cols    <- cols [, -subset, drop = FALSE]
     }
}

palette.swatch()

palette.swatch(n = 26) # show full "Alphabet"; recycle most others

>>>>

<html lang="en">

<head>

<meta charset="UTF-8">

<meta name="viewport" content="width=device-width, initial-scale=1.0">

<title>My Descriptives</title>

<link rel="stylesheet" href="styles.css"> <!-- Link to the CSS file I created for dark mode code chunks -->

</head>

</html>

```{r globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

# Getting started

```{r clean}
rm(list = ls())
```

## Packages

```{r package, hide=TRUE}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

#install.packages("data.table")
require(data.table)  # mainly for faster data handling
# install.packages('xml2')
require(xml2)
# install.packages('rvest')
require(rvest)
require(igraph)
require(ggraph)
require(ggplot2)

@@

require(RColorBrewer)

@@

Functions chunk

```{r functions 1, hide =TRUE}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

More functions

```{r functions 2, hide=TRUE}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

Scholar data

```{r scholar data}
scholars <- fload("./data/processed/scholars_20240924.rda") 
#make sure to lead fload first of course
```

```{r saving scholar output}
# save the output of your function

test  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = c("sociology", "political science"),
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))
```

Ego data

```{r df_ego data}
df_ego <- fload("./data/processed/df_ego_20241108.rda")

@@

# Descriptives - Demographics 
The following graphs represent the segregation of the network based on gender and on H-index for the wave of interest (2015-2018).

@@

descriptives (mean etc.) in whole sample

```{r sum gender}
summary(df_ego$gender)
```

gender counts across whole sample (0 = female, 1 = male)

```{r counts gender-all}
table(df_ego$gender)
```

Histogram: overall gender distribution in sample

```{r histogram gender }
# Convert gender to a factor to avoid errors
df_ego$gender <- as.factor(df_ego$gender)
# Create the histogram with a dark theme and two colors for bars
ggplot(df_ego, aes(x = gender, fill = gender)) +
  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
  scale_fill_manual(
    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
    labels = c("Female", "Male")  # Optional: customize legend labels
  ) +
  labs(
    title = "Gender Distribution",
    x = "Gender\n (0 = female, 1 = male)",
    y = "Count",
    fill = "Gender"  # Legend title
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0"),  # White legend text
    legend.title = element_text(color = "#f0f0f0")  # White legend title
    )

@@

Genders per department (0 = female, 1 = male)

```{r gender per dep.}

@@

descriptives (mean etc.)

```{r summary h index}
summary(df_ego$h_index)
```

Overall(2015-2018)

```{r hist h index}
# Histogram of prestige scores for Wave 1

# Create a data frame for ggplot2 
df_h_index <- data.frame(h_index = df_ego$h_index)

# Generate the histogram with ggplot2
ggplot(df_h_index, aes(x = h_index)) +
  geom_histogram(
    bins = 30,
    fill = "#FFFFB3",  # Bar color
    color = "black"    # Border color for bars
  ) +
  labs(
    title = "Distribution of H-Index from 2015 to 2018",
    x = "H Index",
    y = "Frequency"
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5)  # White centered title
  )

@@

H index per department

```{r table per dep h index}
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```

### 2024-11-23 draftdata.Rmd
modelestimates-GOFs-desresults-darkgraph

-   Csárdi G, Nepusz T, Traag V, Horvát Sz, Zanini F, Noom D, Müller K (2024). \_igraph: Network Analysis and Visualization in R\_. <doi:10.5281/zenodo.7682609> \<[[https://doi.org/10.5281/zenodo.7682609\\\\](https://doi.org/10.5281/zenodo.7682609\\){.uri}]([https://doi.org/10.5281/zenodo.7682609\\](https://doi.org/10.5281/zenodo.7682609\){.uri}){.uri}\>, R package version 2.1.1.9005, \<[[https://CRAN.R-project.org/package=igraph\\\\](https://CRAN.R-project.org/package=igraph\\){.uri}]([https://CRAN.R-project.org/package=igraph\\](https://CRAN.R-project.org/package=igraph\){.uri}){.uri}\>.

>>>>

-   Csárdi G, Nepusz T, Traag V, Horvát Sz, Zanini F, Noom D, Müller K (2024). \_igraph: Network Analysis and Visualization in R\_. <doi:10.5281/zenodo.7682609> \<[[https://doi.org/10.5281/zenodo.7682609\\\\](https://doi.org/10.5281/zenodo.7682609){.uri}](%5Bhttps://doi.org/10.5281/zenodo.7682609%5D(https://doi.org/10.5281/zenodo.7682609)%7B.uri%7D){.uri}\>, R package version 2.1.1.9005, \<[[https://CRAN.R-project.org/package=igraph\\\\](https://CRAN.R-project.org/package=igraph){.uri}](%5Bhttps://CRAN.R-project.org/package=igraph%5D(https://CRAN.R-project.org/package=igraph)%7B.uri%7D){.uri}\>.
